Part B-1

### 2025-09-07 msca-pf-part-b1-template.tex
feat: remove microtype options

% better typography
\usepackage[activate={true,nocompatibility}, % activate protrusion and font expansion
            final,              % enable microtype, use draft to disable
            tracking=true,
            factor=1100,        % more protrusion
            stretch=10,         % smaller values (default 20, 20) to avoid blurring
            shrink=10]{microtype}
\SetTracking{encoding={*}, shape=sc}{40}

>>>>

% better typography
\usepackage[activate={true,nocompatibility}, tracking=true]{microtype}
\SetTracking{encoding={*}, shape=sc}{40}
